Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-08-25 paper.Rmd

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)
n.boot <- 400
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")

@@

data <- example_data(dat = "shock", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

>>>>

#### Curves phase shifted in x-axis direction

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "shift", dir.data)

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
n.boot <- 400

data <- example_data(dat = "smooth", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")

@@

data <- example_data(dat = "shock", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")

data <- example_data(dat = "shift", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```
